Virtualisierung eines Echtzeit-Betriebssystems zur Steuerung eines Roboters mit Schwerpunkt auf die Einhaltung der Echtzeit

### 2024-06-07 Masterarbeit_Robotik_Pamuk.tex
[DRAFT] Kernel Configurations finished

\item \textbf{no\_timer\_check}: Disables the check for broken timer interrupt sources.
\item \textbf{nospectre\_v2, spectre\_v2\_user=off}: Disables mitigations for the Spectre v2 vulnerability.
\item \textbf{kvm.kvmclock\_periodic\_sync=N, kvm\_intel.ple\_gap=0}: These are KVM (Kernel-based Virtual Machine) related parameters.

@@

For CPU isolation, the \texttt{isolcpus} function was used to isolate a performance CPU from the general scheduling algorithms of the operating system. This means that the isolated CPUs will not be used for regular task scheduling, allowing them to be dedicated for the real-time specific tasks or processes. However, the isolcpus function only isolates at the user level and does not affect kernel tasks. Consequently, these kernel tasks and interrupts can still utilize the CPU~\cite{maPerformanceTuningKVMbased}. Output~\ref{output:pse} shows the user and kernel tasks that run on CPU 4. After the isolation, user tasks other than the QEMU process have been removed from running on this CPU. Only few critical kernel threads that are tied to this CPU still take CPU time.

>>>>

	\item \textbf{no\_timer\_check}: Disables the check for broken timer interrupt sources. Broken timer interrupt sources are problems with hardware or software that prevent timer interrupts from working as intended. Such a timer may not generate interrupts at the expected rate or at all. The kernel skips the checks for these broken timer interrupt sources, which can cause unnecessary overhead in a real-time system where every CPU cycle counts.
	\item \textbf{nospectre\_v2, spectre\_v2\_user=off}: These parameters disable mitigations for the Spectre v2 vulnerability. Spectre v2 is a hardware vulnerability that affects many modern microprocessors and can allow malicious programs to access sensitive data they are not supposed to. While this is necessary for security, it has an impact on performance and should be turned off in controlled environments where the risk of exploitation is low.
	\item \textbf{kvm.kvmclock\_periodic\_sync=N, kvm\_intel.ple\_gap=0}: These are KVM (Kernel-based Virtual Machine) related parameters. They disable the periodic synchronization of the kvmclock and set the gap between PLE (Pause Loop Exiting) events to 0. The kvmclock is a paravirtualized clock source provided by KVM to its guest OS and disabling this reduces latency introduced by clock synchronization. By setting the gap to 0, the virtual machine exits the pause loop immediately, which can reduce latency in spinlock-intensive workloads.

@@

\noindent For CPU isolation, the \texttt{isolcpus} function was used to isolate a performance CPU from the general scheduling algorithms of the operating system. This means that the isolated CPUs will not be used for regular task scheduling, allowing them to be dedicated for the real-time specific tasks or processes. However, the isolcpus function only isolates at the user level and does not affect kernel tasks. Consequently, these kernel tasks and interrupts can still utilize the CPU~\cite{maPerformanceTuningKVMbased}. Output~\ref{output:pse} shows the user and kernel tasks that run on CPU 4. After the isolation, user tasks other than the QEMU process have been removed from running on this CPU. Only few critical kernel threads that are tied to this CPU still take CPU time.
